%-------------------------
% Resume in Latex
% Author : Kelves N C
% Based on : Vaishanth R (Overleaf: Resume Professional Template - Software
%Engineer)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\input{config.tex}


%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
{\huge Kelves Nunes da Costa}
\linebreak
\href{mailto:[kelves.nunes@gmail.com]}{kelves.nunes@gmail.com }
\small{$\vert$}
\href{https://www.linkedin.com/in/kelvescosta/}{linkedin.com/in/kelvescosta}
\linebreak
\href{https://github.com/kelvesc}{github.com/kelvesc}
\small{$\vert$}
{Pernambuco, Brasil}
\end{center}


%-----------EDUCATION-----------
\section{\texorpdfstring{EDUCATION}{EDUCATION}}
\resumeSubHeadingListStart

\resumeSubheading
{Universidade Federal Rural de Pernambuco}{Recife, Pernambuco, BR}
{Bachelor of Information Systems}{Jul 2019 - Dec 2025}

\resumeSubheading
{Universidade Federal de Pernambuco}{Recife, Pernambuco, BR}
{Specialization in Computational Photography}{Sep 2023 - Nov 2024}
\textit{\large{with focus on Artificial Intelligence}}
%      {Especialização em Fotografia Computacional}{Sep 2023 - Nov 2024}
%      {\normalsize com foco em Inteligência Artificial}{\newline}

\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{\texorpdfstring{TECHNICAL SKILLS}{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0in, label={}, itemsep=0pt]
%itemsep controls spacing between items
\small{
	\item \textbf{Programming Languages:} {Python, C++, Bash, SQL}
	\item \textbf{Libraries and Tools:} {Git, Numpy, Pandas, PyTorch,
	OpenCV, TensorFlow}
	\item \textbf{Learning:} {CUDA, Halide, Polars, PyTest, scikit-learn}
	\item \textbf{Next Steps:} {AdaptiveCPP, MLFlow, MMCV, NCNN, Robot}
}
\end{itemize}


 %-----------EXPERIENCE-----------
\section{\texorpdfstring{WORK EXPERIENCE}{WORK EXPERIENCE}}
\resumeSubHeadingListStart

\resumeSubheading
{QA Engineer - Automation and Manual}{}
{CIn-Motorola, Pernambuco, Brasil}{Nov 2021 - Today}
\resumeItemListStart
\small{
	\resumeItem{Worked with Product Managers to elucidate requirements and
	usability goals.}
	\resumeItem{Contributed and communicated with overseas development teams.}
	\resumeItem{Designed use cases according to costumer requirements.}
   	\resumeItem{Designed, developed and maintained test cases around identified
   	use cases and executed them.}
   	\resumeItem{Effectively raised and followed up bug reports and managed tasks
   	using JIRA.}
   	\resumeItem{Played a part in several testing strategies such as regression,
   	sanity, integration and exploratory testing.}
	\resumeItem{Documented test strategies, as well as some teams internals
	"how
	to".}
	\resumeItem{Assisted in mentoring for team members to enhancing their
	skills
	and strategy follow up.}
  	}
\resumeItemListEnd

\resumeSubheading
{QA Intern}{}
{CIn-Motorola, Pernambuco, Brasil}{Jan 2021 - Nov 2021}
\resumeItemListStart
\small{
	\resumeItem{Execution of testing strategies aimed at the Android operating
	system.}
	\resumeItem{Raised reports on identified failures and tracked issues using
	Jira.}
	\resumeItem{Made collaborations with overseas development teams.}
	\resumeItem{Proposed and assisted in the implementation of internal
	process
	improvements.}
	\resumeItem{Assisted new team members during their onboard process.}
}
\resumeItemListEnd
  % copy and paste above resumeSubheading block to add more

\resumeSubHeadingListEnd


 %-----------PROJECTS-----------
\section{\texorpdfstring{PROJECTS}{PROJECTS}}

\resumeItemListStart

\resumeItem{\textbf{Image Quality Analysis:} Used pyiqa to assess Neural
Network outputs and leveraged other Neural Nets as evaluators during training.}

\resumeItem{\textbf{Heterogeneous Systems:} Developed custom CUDA kernels for
data management and transformation on NVIDIA GPUs.}

\resumeItem{\textbf{Halide:} Built an image processing pipeline for
cartoonization to showcase Halide’s custom operator capabilities.}

\resumeItem{\textbf{Deep Learning:} Applied MLP for classification and UNet
for
restoration and segmentation.}

\resumeItem{\textbf{OpenCV:} Created an image processing pipeline for
cartoonization.}

% copy and paste above resumeItem block to add more
\resumeItemListEnd


%-----------EXTRACURRICULAR---------------
\section{\texorpdfstring{EXTRACURRICULAR ACTIVITIES}{EXTRACURRICULAR
ACTIVITIES}}
\resumeSubHeadingListStart

\resumeProjectHeading
{Motorola's 50 years anniversary Hackaton}{Nov 2023}
During this 3 days hackaton, our team developed a prototype for a new
Bluetooth
headset feature on Android devices, creating a more immersive and interactive
audio experience. We implemented dynamic sound panning and displacement
effects, adjusted in real time based on the user's movement relative to the
paired device, enhancing the sense of presence and realism.

\resumeProjectHeading
{SEBRAE's Early Stage program} {Mar 2021}
During 6 weeks of Catalisa ICT I worked on modeling and validating the
business
model of MuoCare, a solution based on AI models for disease detection in dairy
cattle.

% copy and paste above \resumeProjectHeading block to add more

\resumeSubHeadingListEnd


%-----------Publications---------------
\section{\texorpdfstring{PUBLICATIONS}{PUBLICATIONS}}

{Unfortunately, I have not had the pleasure of participating in the
publication
of a published article. However, I hope to be able to fulfill this wish in the
near future. For any references, my Lattes resume is available through this
link}
\href{[http://lattes.cnpq.br/0278549043500928]}{\color{blue}\underline{here}}


%%%%%%%%%%%%  RESUME ENDS HERE  %%%%%%%%%%%%
\end{document}